---
title: "Lab 3"
author:
- Marquise Baggiore
- Jacob Schmidt
- Ryan Sears
- Wenquan Lai
output:
  pdf_document: default
  fig_caption: yes
  keep_tex: yes
  html_document:
    df_print: paged
---


```{r include = FALSE, echo = FALSE}
library(MASS)
library(leaps)
library(caret)
library(knitr)
tinytex::install_tinytex()

ames_data <- ames_data <- read.csv('ames.csv', header = TRUE, sep=',')
data <- ames_data[, sapply(ames_data, is.integer)]
data_om <- na.omit(data)

# dropping data
drops <- c('OverallCond', 'OverallQual')
df <- data_om[, !(names(data_om) %in% drops)]

num_obs <- nrow(df)
train_index <- sample(num_obs, size=trunc(.5 * num_obs))
train_data <- df[train_index, ]
test_data <- df[-train_index, ]

traincontrol <- trainControl(method='cv', number=10)
```

<br>
<br>
<br>

```{r echo = FALSE, include=FALSE}
# predicting sales price
model_test <- train(SalePrice ~ ., data=test_data,
                     method='leapForward',
                     tuneGrid=data.frame(nvmax=3),
                     trControl= traincontrol)

sales_prediction <- predict(model_test)
# sales prediction mean : $183703.3
# actual saleprice mean : $185506.2
# used 21 indepndent variables / predictors

# rmse for train and test
model_train <- train(SalePrice ~ ., data=train_data,
                    method='leapForward',
                    tuneGrid=data.frame(nvmax=3),
                    trControl= traincontrol)
rmse_train <- model_train$results['RMSE']
# train rmse = 48348.24
rmse_test <- model_test$results['RMSE']
# test rmse = 38932.07
```

We arrived at this model by originally plotting our RMSE's found by using Forward Selection.
<br>
<br>
We aimed to pick the max amount of regressors that gave us the minimized the RMSE. 
<br>
<br>
When we applied this to our prediction, we got an estimated mean Sale Price that was very close to the actual Sale Price mean. 
<br>
<br>
We then noticed the Test RMSE was much larger than the Train RMSE. This was a result of overfitting our model. 
<br>
<br>
We then adjsuted the model to make sure the amount of regressors chosen did not lead to overfitting. 
<br>
<br>
The end result was a very similar Sales Price mean, the difference between our estimated Sale Price Mean and Actual Sale Price Mean was $3,162.42
<br>
<br>
<br>
```{r echo = FALSE}
df2 <- data.frame(A=mean(sales_prediction), B=mean(df$SalePrice), C=rmse_train, D=rmse_test)
kable(df2, col.names = c('Predicted Mean Sale Price ', 'Actual Mean Sale Price ', 'Train RMSE ', 'Test RMSE'))
```







